Geometrization of characters of tori over non-Archimedean local fields

### 2013-08-12 shanghai.tex
Moved more material in from the base change file; I'll work it into the draft.

@@

@@

\David{We should add a discussion of why we care about the transfer principle.}
We recall the notion of $N$-congruent tori from \cite[\S 2]{CY}.  Suppose $T$ and $T'$
are tori over non-Archimedian local fields $K$ and $K'$, splitting over $L$ and $L'$ respectively.

>>>>

\Clifton{Return to finite and bounded character sheaves, explaining why our definition is the right one. Also explain why we don't think of local systems as representations of a fundamental group.}

\section{Restriction of scalars}

In the opposite direction, there is a canonical closed immersion of $k$-schemes
$G \hookrightarrow \Res_{k'/k}(G_{k'})$ \cite[\S 7.6]{BLR}.  Pullback yields a functor
\[
\GC(\Res_{k'/k}(G_{k'})) \xrightarrow{\iota} \GC(G).
\]
\begin{proposition} \label{prop:csbe}
The following diagram commutes, where the bottom map is induced by the inclusion $G(k) \hookrightarrow G(k')$:
\[
\begin{tikzcd}
\GCiso{\Res_{k'/k}(G_{k'})} \arrow[two heads]{r}{\iota} \dar{t_{\Res_{k'/k}(G_{k'})}} & \GCiso{G} \dar{t_G} \\
\Hom(G(k'), \EEx) \arrow[two heads]{r} & \Hom(G(k), \EEx).
\end{tikzcd}
\]
\end{proposition}

Now suppose that $G'$ is an abelian group scheme over $k'$, satisfying the conditions of Theorem \ref{thm:snake}.
There is a canonical isomorphism between $G'(k')$ and $(\Res_{k'/k}G')(k)$;
we now describe the corresponding functor from
$\GC(G')$ to $\GC(\Res_{k'/k}G')$.  The base change $(\Res_{k'/k}G')_{k'}$ of $\Res_{k'/k}G'$ to $k'$
decomposes into a product of copies of $G'$, indexed by elements of $\Gal(k'/k)$:
\[
(\Res_{k'/k}G')_{k'} \cong \prod_{\Gal(k'/k)} G'.
\]
The component corresponding to the identity element yields a natural inclusion 
\[
G' \hookrightarrow (\Res_{k'/k}G')_{k'}
\]
of $k'$-schemes.  The definition of base change yields a map of $k$-schemes
\[
(\Res_{k'/k}G')_{k'} \to \Res_{k'/k}G'.
\]
Consecutive pullback along these maps yields a functor
\[
\GC(G') \to \GC(\Res_{k'/k}G').
\]

\begin{proposition}
  Then the following diagram commutes:
\[
\begin{tikzcd}
\GCiso{G'} \dar{t_{G'}} \rar & \GCiso{\Res_{k'/k} G'} \dar{t_{\Res_{k'/k} G'}} \\
 \Hom(G'(k'), \EEx) \rar & \Hom((\Res_{k'/k}G')(k), \EEx)
\end{tikzcd}
\]
\end{proposition}

@@

\section{Base change over the local field}

We have already seen that the trace of Frobenius defines a canonical isomorphism 
$t_T : \GCiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$. 
In this section we expand on the canonicity of this group isomorphism 
by showing that it is a natural transformation. We also show

\begin{proposition}
The isomorphism $t_T : \GCiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$ 
is a natural transformation between the following two contravariant functors 
from the category of algebraic tori over $K$ to the category of abelian groups: 
\begin{enumerate}
\item $T \mapsto \GCiso{\GN{T}}$
\item $T \mapsto \Hom_\text{ad}(T(K),\EEx)$.
\end{enumerate}
\end{proposition}

\Clifton{I think I can prove this proposition without too much difficulty.}
\begin{proof}
\end{proof}

Let $L/K$ be a finite Galois extension and let $K'/K$ be the maximal unramified subextension, with residue field $k'$.  If $T$ is a torus over $K$, write $\TL$ for the N\'eron model of the base change $T_L$.  Then there is a canonical isomorphism
\[
\Res_{k'/k} \Gr(\TL) \cong \Gr(\underline{\Res_{L/K}(T_L)}).
\]
The natural inclusion $T \hookrightarrow \Res_{L/K} T_L$ induces a map of $k$-schemes
\[
\GN{T} \hookrightarrow \Res_{k'/k} \Gr(\TL)
\]
and thus a functor on character sheaves through pullback.

\begin{proposition}
The following diagram commutes:
\[
\begin{tikzcd}
\GCiso{\Res_{k'/k} \Gr(\TL)} \arrow[two heads]{r} \dar & \GCiso{\GN{T}} \dar\\
\Hom(T(L), \EEx) \arrow[two heads]{r} & \Hom(T(K), \EEx)
\end{tikzcd}
\]
\end{proposition}

@@

\David{We should add a discussion of why we care about the transfer principle.}

The techniques in this paper apply to all non-Archimdean local fields $K$ with residue field $k$, and to all algebraic tori $T$ over $K$, without placing any restrictions on the characteristic of $K$ or on the ramification of $T$. Because of this, it is natural to ask if we can compare geometrized characters of $T$

We recall the notion of $N$-congruent tori from \cite[\S 2]{CY}.  Suppose $T$ and $T'$
are tori over non-Archimedian local fields $K$ and $K'$, splitting over $L$ and $L'$ respectively.
